 

### 2022-03-07 doc/manuscript/Dow_manuscript_Nature.Rmd
remove arrows for non-biologically sig relationships

![**Figure 1 | Summary of temperate deciduous tree growth responses to warmer spring temperatures.** (a) Schematic illustrating parameters of interest and summarizing predominant responses of each to warmer maximum temperatures during a 'critical temperature window', defined as the period with the strongest control over $DOY_{25}$; (b) Variable definitions and summary of responses to warmer spring temperatures at two temperate forests -- Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest -- and for two groups of broadleaf deciduous species (RP=ring porous; DP=diffuse porous), where up and down arrows indicate significant (p<0.05) increases and decreases, respectively, '-' indicates no significant correlation, and 'mixed' indicates a mix of significant and non-significant correlations, often in different directions.](tables_figures/schematic_summary_with_table.png){ width=70% }

>>>>

![**Figure 1 | Summary of temperate deciduous tree growth responses to warmer spring temperatures.** (a) Schematic illustrating parameters of interest and summarizing predominant responses of each to warmer maximum temperatures during a 'critical temperature window', defined as the period with the strongest control over $DOY_{25}$; (b) Variable definitions and summary of responses to warmer spring temperatures at two temperate forests -- Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest -- and for two groups of broadleaf deciduous species (RP=ring porous; DP=diffuse porous), where up and down arrows indicate increases and decreases that are significant both statistically (p<0.05) and biologically (effect size >3%/$^\circ$C), '-' indicates no significant correlation, and 'mixed' indicates a mix of significant and non-significant correlations, often in different directions.](tables_figures/schematic_summary_with_table.png){ width=70% }

### 2022-03-07 doc/manuscript/tables_figures/schematic_summary.Rmd
remove arrows for non-biologically sig relationships

#add footnote: 
#kableExtra::footnote(number = c("'RP' and 'DP' refer to ring- and diffuse- porous species, respectively", "'-' and '+' = significant negative or positive response, respectively; 'n.s.'= no significant correlation"), footnote_as_chunk = FALSE, threeparttable=TRUE, escape = FALSE)
```
*While this result was statistically significant, effect size was small and considered not biologically significant

>>>>

#add footnote: 
#kableExtra::footnote(number = c("'RP' and 'DP' refer to ring- and diffuse- porous species, respectively", "'-' and '+' = significant negative or positive response, respectively; 'n.s.'= no significant correlation"), footnote_as_chunk = FALSE, threeparttable=TRUE, escape = FALSE)
```
